EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-08-07 05_examples.tex
Updated text and bib to SciPost proofs.

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section, we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ) model.
As shown in Ref. \cite{Amaricci2023PRB}, this model exhibits an excitonic phase at moderate
interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}

>>>>

\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
In this section, we focus on the DMFT solution of the interacting
Bernevig-Hughes-Zhang (BHZ) model.
As shown in Ref. \cite{Amaricci2023PRB}, this model exhibits an excitonic phase at moderate
interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2022NP,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
